Comparison of Two Second Order Traffic Flow Models

### 2015-03-10 Presentation/presentation.tex
Updated slides again
Adding edits to presentation.

\documentclass{beamer}
\usepackage{subfigure}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{listings}
\usepackage{multicol}
\usepackage{media9}

@@

\title[Short title]{Beep Beep!} % The short title appears at the bottom of every slide, the full title is only on the title page

@@

\begin{frame}
\frametitle{AR: Hugoniot Loci}
In order to consider the Hugoniot loci for this system we must first write the system in conservation form. 
With some manipulation, we can get the system
\begin{align*}
&\partial_t\rho + \partial_x(\rho v) = 0, \\
&\partial_t \left(\rho\left(v + p(\rho )\right)\right) + \partial_x \left( \rho v\left(v + p(\rho )\right)\right) = 0.
\end{align*}
This can be rewritten as $q_t + f(q)_x = $ by defining
\begin{align*}
q = \left[ \begin{matrix}
\rho \\ y
\end{matrix}\right], \hspace{0.3in}
f(q) = \left[ \begin{matrix}
v\rho \\
vy
\end{matrix}\right].
\end{align*}
where $y = \rho\left(v + p(\rho )\right)$.
\end{frame}

@@

To illustrate a couple of examples where the AR model preforms better than the PW model, consider two different examples: 
\begin{table}[t]
\caption{Initial values used in examples 1 and 2.}
\begin{center}
\begin{tabular}{| c | c c  c c|}
\hline
& $v_l$ & $\rho_l $ & $v_r$ & $\rho_r $\\
\hline
Example 1 & 0.2 & .03 & 0.3 & 0.4 \\
Example 2 & 0 & 0 & 0.3 & 0.4\\
\hline
\end{tabular}
\end{center}
\end{table}
\end{frame}

\begin{frame}
\frametitle{Example 1}
The solution to the Riemann problem is:
\begin{figure}[h!]
 \centering
 \subfigure[Solution from the AR model.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/AR_example1.jpg}
   }
    \subfigure[Solution from the PW model.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/PW_example1.jpg}
   }
\end{figure}
\end{frame}

\begin{frame}
\frametitle{Example 1}
\begin{center}
\begin{multicols}{2}%
AR model:
\includemedia[
  width=0.9\linewidth,
  height=0.7\linewidth,
  activate=pageopen,
  addresource=AR_Example1Movie.mp4,
  flashvars={source=AR_Example1Movie.mp4}
]{}{VPlayer.swf}
\vfill
\columnbreak
PW Model:
\includemedia[
  width=0.9\linewidth,
  height=0.7\linewidth,
  activate=pageopen,
  addresource=PW_Example1Movie.mp4,
  flashvars={source=PW_Example1Movie.mp4}
]{}{VPlayer.swf}
\end{multicols}
\end{center}
\end{frame}

\begin{frame}
\frametitle{Example 2}
The solution to the Riemann problem is:

@@

\begin{frame}
\frametitle{Example 2}
\begin{center}
\begin{multicols}{2}%
AR model:
\includemedia[
  width=0.9\linewidth,
  height=0.7\linewidth,
  activate=pageopen,
  addresource=AR_Example2Movie.mp4,
  flashvars={source=AR_Example2Movie.mp4}
]{}{VPlayer.swf}
\vfill
\columnbreak
PW Model:
\includemedia[
  width=0.9\linewidth,
  height=0.7\linewidth,
  activate=pageopen,
  addresource=PW_Example2Movie.mp4,
  flashvars={source=PW_Example2Movie.mp4}
]{}{VPlayer.swf}
\end{multicols}
\end{center}
\end{frame}

@@

%----------------------------------------------------------------------------------------
\bibliography{presentation}{}
\bibliographystyle{plain}
\end{document}

>>>>

\documentclass{beamer}
\usepackage{subfigure}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{listings}
\usepackage{multicol}
\usepackage{media9}
\usepackage{graphicx}
\usepackage{mathtools}

@@

\title[Short title]{Comparison of Two Second Order Traffic Flow Models} % The short title appears at the bottom of every slide, the full title is only on the title page

@@

\begin{frame}
\frametitle{AR: Hugoniot Loci}
In order to consider the Hugoniot loci for this system we must first write the system in conservation form. 
With some manipulation, we can get the system
\begin{align*}
&\partial_t\rho + \partial_x(\rho v) = 0, \\
&\partial_t \left(\rho\left(v + p(\rho )\right)\right) + \partial_x \left( \rho v\left(v + p(\rho )\right)\right) = 0.
\end{align*}
This can be rewritten as $q_t + f(q)_x = 0$ by defining
\begin{align*}
q = \left[ \begin{matrix}
\rho \\ y
\end{matrix}\right], \hspace{0.3in}
f(q) = \left[ \begin{matrix}
v\rho \\
vy
\end{matrix}\right].
\end{align*}
where $y = \rho\left(v + p(\rho )\right)$.
\end{frame}

@@

To illustrate a couple of examples where the AR model preforms better than the PW model, consider two different examples: 
\begin{table}[t]
\caption{Initial values used in examples 1 and 2.}
\begin{center}
\begin{tabular}{| c | c c  c c|}
\hline
& $v_l$ & $\rho_l $ & $v_r$ & $\rho_r $\\
\hline
Example 1 & 0.2 & 0.3 & 0.3 & 0.4 \\
Example 2 & 0 & 0 & 0.3 & 0.4\\
\hline
\end{tabular}
\end{center}
\end{table}
\end{frame}

\begin{frame}
\frametitle{Example 1}
Initial Conditions:
\begin{table}[t]
\begin{center}
\begin{tabular}{| c c  c c|}
\hline
$v_l$ & $\rho_l $ & $v_r$ & $\rho_r $\\
\hline
0.2 & 0.3 & 0.3 & 0.4 \\
\hline
\end{tabular}
\end{center}
\end{table}

The solution to the Riemann problem is:
\begin{figure}[h!]
 \centering
 \subfigure[Solution from the AR model.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/AR_example1.jpg}
   }
    \subfigure[Solution from the PW model.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/PW_example1.jpg}
   }
\end{figure}
\end{frame}

\begin{frame}
\frametitle{Example 1}
Initial Conditions:
\begin{table}[t]
\begin{center}
\begin{tabular}{| c c  c c|}
\hline
$v_l$ & $\rho_l $ & $v_r$ & $\rho_r $\\
\hline
0.2 & 0.3 & 0.3 & 0.4 \\
\hline
\end{tabular}
\end{center}
\end{table}

\begin{center}
\begin{multicols}{2}%
AR model:
\includemedia[
  width=0.9\linewidth,
  height=0.7\linewidth,
  activate=pageopen,
  addresource=AR_Example1Movie.mp4,
  flashvars={source=AR_Example1Movie.mp4}
]{}{VPlayer.swf}
\vfill
\columnbreak
PW Model:
\includemedia[
  width=0.9\linewidth,
  height=0.7\linewidth,
  activate=pageopen,
  addresource=PW_Example1Movie.mp4,
  flashvars={source=PW_Example1Movie.mp4}
]{}{VPlayer.swf}
\end{multicols}
\end{center}
\end{frame}

\begin{frame}
\frametitle{Example 2}
Initial Conditions:
\begin{table}[t]
\begin{center}
\begin{tabular}{| c c  c c|}
\hline
$v_l$ & $\rho_l $ & $v_r$ & $\rho_r $\\
\hline
0 & 0 & 0.3 & 0.4 \\
\hline
\end{tabular}
\end{center}
\end{table}

The solution to the Riemann problem is:

@@

\begin{frame}
\frametitle{Example 2}
Initial Conditions:
\begin{table}[t]
\begin{center}
\begin{tabular}{| c c  c c|}
\hline
$v_l$ & $\rho_l $ & $v_r$ & $\rho_r $\\
\hline
0 & 0 & 0.3 & 0.4 \\
\hline
\end{tabular}
\end{center}
\end{table}

\begin{center}
\begin{multicols}{2}%
AR model:
\includemedia[
  width=0.9\linewidth,
  height=0.7\linewidth,
  activate=pageopen,
  addresource=AR_Example2Movie.mp4,
  flashvars={source=AR_Example2Movie.mp4}
]{}{VPlayer.swf}
\vfill
\columnbreak
PW Model:
\includemedia[
  width=0.9\linewidth,
  height=0.7\linewidth,
  activate=pageopen,
  addresource=PW_Example2Movie.mp4,
  flashvars={source=PW_Example2Movie.mp4}
]{}{VPlayer.swf}
\end{multicols}
\end{center}
\end{frame}

@@

%----------------------------------------------------------------------------------------
\begin{frame}
\frametitle{Bibliography}
\bibliography{presentation}{}
\bibliographystyle{plain}
\end{frame}

\end{document}
